WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2021-01-01 method/sec_5-data_preprocess.tex
After Dr. Dilum reviewed the Viva thesis

The data preprocess functionalities support simple generic mathematical function models. Each extension is considered as a mathematical function that can take \texttt{p} input timeseries variables and output \texttt{n} timeseries variables after applying the given function. Further, the system supports to provide a bind constant as configurations to the extension at the time of preprocessing. Thus, users can change the behavior of an existing function by providing different bind constants at the time of creating new triggers for an extension and produce different behaviors.

\subsection{Interpolation}
The interpolation module generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature, based on information available at nearby locations.

\subsubsection{Serial Interpolation}
During serial interpolation, we use interpolation to fill any gaps in a timeseries. The interpolation module will only consider a single timeseries, which is itself in filling these gaps.

@@

\subsubsection{Spatial Interpolation}
During spatial interpolation, we use interpolation to either fill gaps in timeseries or to create a new timeseries for a location using data from other (spatially distributed) locations. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation of time interval transformation and shifting the series in time specific hydro-meteorological transformation such as stage discharge relationships.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregration.}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}
Checks for counting reliable, doubtful, unreliable, and missing values.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/validation.pdf}
    \caption{Timeseries data validation.}
    \label{fi:validation}
\end{figure}

>>>>

The data preprocess functionalities support simple generic mathematical function models. Each extension is considered as a mathematical function that can take \texttt{p} input timeseries variables and output \texttt{n} timeseries variables after applying the given function. Further, the system supports to provide a bind constant as configurations to the extension at the time of preprocessing. Thus, users can change the behavior of an existing function by providing different bind constants at the time of creating new triggers for an extension and produce different behaviors. Next, we explain how to derive interpolation, transformation, and validation functions using the generic mathematical function model described above.

\subsection{Interpolation}
The interpolation extension generates data at desired locations or desired data points using a serial or spatial interpolation technique. It is used to fill gaps in linear measured data and to derive spatially distributed data for weather timeseries, such as precipitation and temperature based on information available at nearby locations. Here, we will discuss two types of interpolation, such as serial interpolation and spatial interpolation, below.

\subsubsection{Serial Interpolation}
During serial interpolation, we use interpolation to fill any gaps in a linear timeseries. The interpolation module will only consider a single timeseries, which is itself filling the missing data points. For example, as seen in Figure \ref{fi:serial_interpolation}, there can be timeseries that has data points of temperature collected using a weather station. There can be missing data in this timeseries, and we can use a simple linear interpolation algorithm to fill the missing values based on the existing data points.

@@

\subsubsection{Spatial Interpolation}
During spatial interpolation, we use interpolation to either fill gaps in timeseries or create a new timeseries for a location using data from other (spatially distributed) locations' timeseries. Spatial interpolation can also be applied for sampling scalar timeseries from grid timeseries, for re-sampling grids, or for creating grids from timeseries data. For example, let us assume that there are precipitation timeseries data available for location \textit{A} and location \textit{B} as shown in Figure \ref{fi:spatial_interpolation}. Then we want to calculate the mean precipitation of nearby locations using these two timeseries. We can use the spatial interpolation to get the mean precipitation of nearby locations.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/spatial_interpolation.pdf}
    \caption{Spatial interpolation.}
    \label{fi:spatial_interpolation}
\end{figure}

\subsection{Transformation}
Simple arithmetic manipulation of time interval transformation and shifting the series in time-specific hydro-meteorological transformation such as stage-discharge relationships are considered transformation. For example, as seen in Figure \ref{fi:transformation}, there can be a timeseries of precipitation with 1-minute sample data. There will be a model requirement that needs hourly data. Therefore, we need to accumulation data manipulation to create a timeseries of hourly data using 1-minute sample data.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/transformation.pdf}
    \caption{Time interval aggregation.}
    \label{fi:transformation}
\end{figure}

\subsection{Validation}
Validation functions check for counting reliable, doubtful, unreliable, and missing values. The weather stations can produce invalid observations due to technical errors in the sensors of the devices. If we feed those values directly to the models, the models will produce inaccurate forecasting. To avoid that, we need to modify or flag those values before feeding them to the numerical models. As seen in Figure \ref{fi:validation} We can use validation extensions to modify or flag invalid data. For example, a weather station can record temperature above 70 celsius due to sensor error or calibration issues. However, in the real world, it is not possible to have such a temperature in nature. Thus, we need to flag such temperature issues and repair the weather station as soon as possible.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{method/data_preprocess/validation.pdf}
    \caption{Timeseries data validation.}
    \label{fi:validation}
\end{figure}

### 2021-01-01 method/sec_7-summary.tex
Proof read: Chapter 1
After Dr. Dilum reviewed the Viva thesis

Throughout this Chapter, we discussed the methodology of designing and implementing the \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

>>>>

Throughout the \cref{ch:method}, we discussed the methodology of designing and implementing \acrshort{wdias} based on the concepts studied in the literature review of \cref{ch:literature}. We used microservice architecture over \acrshort{soa} with an \acrshort{esb} to avoid the drawback of streaming bulk data through an \acrshort{esb}. To take the full advantage of using the microservices architecture, we moved to container orchestration based architecture rather than building tightly coupled microservices with the actor model. 
While implementing the import and export modules, those modules followed the microservice architecture style of \emph{smart endpoints and dumb pipes}. Each microservice is implemented as a containerized application that can deploy independent of other microservices. Also, we used the microservice architecture pattern of \emph{database per service} by combining different types of database systems to create the \acrshort{wdias} database structure. Further, we provided a comprehensive extension module system that allows users to preprocess data by creating new triggers without any downtime for system configuration. We used a geo indexing mechanism to support geo-search queries and indexed the timeseries metadata to support the search for any timeseries in \acrshort{wdias}.

### 2021-01-01 results/sec_3-observations.tex
After Dr. Dilum reviewed the Viva thesis

This section includes the observations based on the test plans discussed in \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}. Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans with 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size for scalar and vector timeseries. \gkc{For grid timeseries, we performed the load test plans with ASCII grid file as data for each time step which has the size of 52 kilobyte. On average, each sample grid data for 60-minute data requests consist of 1.2 megabyte, 30-minute data requests consist of 2.4 megabyte, and 15-minute data requests consist of 4.9 megabyte}. Then we perform another round of 15-minute data with enabling auto-scaling for the higher resource utilized microservices.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Response time vs threads while load testing with hourly data.}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads for 60-minute data requests. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. The above graph shows the scalability of the \acrshort{wdias} since the system is able to process more requests without a significant change in the latency. When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving scalar and vector data. The performance degrades because those data handles on-demand and depends on the timeseries database performance.

@@

\cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second. This graph further proves that the system was able to handle the increasing workload without any significant change in the delay.

@@

Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files per each insertion request for the grid data type. Also, the test plan performed round up to \num{311e3} number of sample requests, which is almost similar to the number of samples processed with hourly resolution data.

@@

\cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} with 30-minute resolution data. The results are almost similar to the observations in \cref{subse:obs_test_plan_all_60min}. Even though we doubled the request size, \acrshort{wdias} was able to keep the performance almost the same instead of increasing the latency twice.

@@

During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request for the grid data type. The size of each request is four times larger than the 60-minute resolution data. Here also, the test plan performed approximately \num{311e3} of sample requests, which are almost similar to sample requests made during 60-minute and 30-minute resolution data.
\begin{table}[ht]
\caption{Throughput and latency of load test with 15-minute data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}

\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} of the test plan with 15-minute resolution data. When compared to the observations from the performance test with 30-minute data, the request latency also increased for all sample requests. Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests. One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the database has effects on the database reads. Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues. Also, the system provided the same throughput as with 60-minute and 30-minute resolution data.

@@

\cref{fi:test_obs_all_15m_response_vs_threads} shows the latency against the number of active threads for the test plan with 15-minute resolution data. As per the graph, the system was able to keep the response latency constant while increasing the number of active threads. However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of timeseries data. The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data. With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads.

@@

\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput is \emph{active threads per second / thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
It shows the statistical maximum possible number of transactions based on the number of users accessing the application.
By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

@@

\cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_15min}. If we analyzed the performance of the auto-scaling enabled microservice, the average grid data insertion latency was reduced from 91 milliseconds to 87 milliseconds. Also, we can notice that the error percentage reduced from 1.42\% to 0.18\%. Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency. Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
    \caption{Latency against server hits while load testing with 15-minute of data with enabled auto-scaling.}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute data while auto-scaling enabled for K8s. According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
When compared to \cref{fi:test_obs_all_15m_latency} without auto-scaling, we can see lesser latency spikes throughout the test period.

@@

\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against the number of active threads. When compared to \cref{fi:test_obs_all_15m_throughtput} without auto-scaling, the estimated throughput with a higher number of active threads becomes stable, according to the graph. Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active users. During the next paragraphs, we discuss the resource usage while running the test plan while enabling the auto-scaling.

>>>>

This section includes the observations based on the test plans discussed in \cref{se:test_plan}, and the experimental system setup explained in \cref{se:workload}. Sections \ref{subse:obs_test_plan_all_60min} to \ref{subse:obs_test_plan_all_auto_15min}, we discuss the observations collected with performing the load test plans with 60-minute data (24 data points per request), 30-minute data (48 data points per request), and 15-minute data (96 data points per request) by varying the request size for scalar and vector timeseries. For grid timeseries, we performed the load test with ASCII grid file as data for each time step (with the size of 52 KB). On average, each sample grid data for 60-minute data requests consist of 1.2 MB, 30-minute data requests consist of 2.4 MB, and 15-minute data requests consist of 4.9 MB. Then we perform another round of 15-minute data with enabling auto-scaling for the higher resource utilized microservices.

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{results/obs/all/obs_all_60m_response_times_vs_threads.png}
    \caption{Response time vs threads while load testing with hourly data.}
    \label{fi:test_obs_all_60m_response_vs_threads}
\end{figure}
\cref{fi:test_obs_all_60m_response_vs_threads} shows the response time against the number of active threads for 60-minute data requests. As the graph shows, the response time kept the same while increasing the number of active threads against each test case. The above graph shows the scalability of the \acrshort{wdias} since the system is able to process more requests without a significant change in the latency. When the number of active threads increased more than 122, \cref{fi:test_obs_all_60m_response_vs_threads} shows uncertainty in the inserting and retrieving scalar and vector data. The performance degrades because those data handles on-demand and depends on the timeseries database performance. 
However, when the request sizes are smaller, \acrshort{wdias} was able to perform insert and retrieval of grid data with the same latency.

@@

\cref{fi:test_obs_all_60m_latency} graph provides a better overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second. This graph further proves that the system was able to handle the increasing workload without any significant change in the delay. The stepped red colour graph for server hits per second shows the number of requests that was sent by the load test with time. Other horizontal lines with spikes show the latency for each of test case, such as insertion and retrieval of scalar, vector, and grid data with time.

@@

Next, we performed the test plan with 30-minute resolution data, which means 48 data points per each request for the scalar and vector data types, and 48 ASCII grid files with 2.4 MB of size per each insertion request for the grid data type. Also, the test plan performed round up to \num{311e3} number of sample requests, which is almost similar to the number of samples processed with hourly resolution data. That means \acrshort{wdias}-based system was able to process same number of request while increasing the request size with providing higher throughput.

@@

\cref{tab:obs_all_30_min_summary} shows the response latency summary details and \acrshort{rps} with 30-minute resolution data. The results are almost similar to the observations in \cref{subse:obs_test_plan_all_60min}. Even though we doubled the request size, \acrshort{wdias} was able to keep the performance almost the same instead of increasing the latency twice.
Insertion and retrieval of scalar and vector data increased by 1 millisecond on average. However, the grid data insert latency increased from 23 milliseconds to 40 milliseconds. Such doubling of latency is expected, as the grid data size was increased from 1.2 MB to 2.4 MB, and it is taking time to stream the data into \acrshort{wdias}-based system. Retrieval of grid data also increased by 22 milliseconds, because during the test cases, we try to retrieve the inserted grid data in a different format, but the export data size also gets increased due to the increase of the insert grid data size.

@@

During this section, we performed the test plan with 15-minute resolution data, which means 96 data points per each request for the scalar and vector data types, and 96 ASCII grid files per each insertion request with the size of 4.9 MB for the grid data type. The size of each request is four times larger than the 60-minute resolution data. Here also, the test plan performed approximately \num{311e3} of sample requests, which are almost similar to sample requests made during 60-minute and 30-minute resolution data. This means \acrshort{wdias}-based system was able to increase the throughput while increasing load with the request size, and processed the same amount of requests within the elapsed time.

\begin{table}[ht]
\caption{Throughput and latency of load test with 15-minute data}
\footnotesize
\begin{tabulary}{\linewidth}{|L|R|R|R|R|R|R|R|R|}
\hline
\textbf{Label} & \textbf{Samples} & \textbf{Avg} & \textbf{Min} & \textbf{Max} & \textbf{90\% Line} & \textbf{Std.Dev.} & \textbf{Error} & \textbf{RPS} \\ \hline
Insert Timeseries & 71775 & 30 & 12 & 1719 & 41 & 51.71 & 0.00\% & 40.5 \\ \hline
Retrieve Timeseries & 71736 & 23 & 8 & 1623 & 32 & 50.18 & 0.00\% & 40.6 \\ \hline
Insert Grid & 7975 & 91 & 77 & 279 & 112 & 19.58 & 1.42\% & 4.5 \\ \hline
Retrieve Grid & 7972 & 118 & 80 & 876 & 165 & 56.15 & 0.00\% & 4.5 \\ \hline
Query: Location & 71749 & 3 & 2 & 130 & 4 & 2.32 & 0.00\% & 40.5 \\ \hline
\textbf{TOTAL} & 310934 & 134 & 0 & 1719 & 503 & 206.40 & 0.04\% & 175.4 \\ \hline
\end{tabulary}
\label{tab:obs_all_15_min_summary}
\end{table}

\cref{tab:obs_all_15_min_summary} shows the response latency summary details and \acrshort{rps} of the test plan with 15-minute resolution data. When compared to the observations from the performance test with 30-minute data, the request latency also increased for all sample requests. The scalar and vector data insertion increased by 1 milliseconds, and retrieval of those data increased significantly by doubling the latency. Also, the standard deviation of retrieval timeseries data increased by a considerable amount for all the data type's sample requests. One of the reasons for increasing the retrieval data delay was while performing heavy database writes on the InfluxDB database instance has effects on the database reads. The grid data insert and retrieve latency also doubled approximately because the stream data size increase by a factor of two compared to 30-minute data. Noticeably, the error rate of inserting grid data increased up to 1.42\%. Even though we increased the request data size by four times higher, the system was able to handle all requests without significant performance issues. Also, the system was able to process same number of request as with 60-minute and 30-minute resolution data while increasing the throughput of the system with the request size.

@@

\cref{fi:test_obs_all_15m_response_vs_threads} shows the latency against the number of active threads for the test plan with 15-minute resolution data. As per the graph, the system was able to keep the response latency constant while increasing the number of active threads. However, when the number of active threads became higher, there was a disturbance with the response delay during the insertion and retrieval of scalar and vector timeseries data. As mentioned above, this may happened due to the system reaching its maximum capacity as per the allocated resources, or caused by heavy database read and writes on the InfluxDB free database version. The latency of insert and retrieval of grid timeseries data increased twice when compared to 30-minute resolution data. With a larger request size, we can notice the latency also increased by a smaller factor when we increased the number of active threads. When compared to the load testing with 60-minute and 30-minute data, we can see 192 active threads used by the JMeter to maintain the \acrshort{rps}. When we increase the request size, the latency also increases. Then the active threads have to wait for the response from the system rather than doing any other work. To maintain the server hits, the JMeter has to spawn more active threads.

@@

\cref{fi:test_obs_all_15m_throughtput} shows the total server's transaction throughput against the number of active threads.
The formula for total server transaction throughput is \emph{active threads per second / one thread response time} \cite{ApacheSoftwareFoundationJMeter:Plugin}.
It shows the statistical maximum possible number of transactions based on the number of active threads accessing the application at a given time. This estimates the transaction throughput based on the latency of requests against the number of active threads at a given time. We can assume that the highest number of active threads occur at the peak time of the load testing. However, the number of latency samples are limit with the higher number of active threads. Consequently, in \cref{fi:test_obs_all_15m_throughtput} we can see missing data points, and spikes with graph drawing with available data points. Further we can analyze this graph against \cref{fi:test_obs_all_15m_response_vs_threads}, and derive this output based on latency fluctuation in that graph. By combining the \cref{fi:test_obs_all_15m_latency}, this graph shows that the throughput of the system gets increased without much change in the latency, thus it proves the scalability of the \acrshort{wdias}.

@@

\cref{tab:obs_all_auto_15_min_summary} shows the response latency summary details and \acrshort{rps} as explained in \cref{subse:obs_test_plan_all_15min}. If we analyzed the performance of the auto-scaling enabled microservice, the average grid data insertion latency was reduced from 91 milliseconds to 87 milliseconds. Also, we can notice that the error percentage reduced from 1.42\% to 0.18\%. Since the standard deviation also reduced, we can conclude that the latencies are closer to the average latency. Further, these improvements in insert grid timeseries data seem to affect the output of retrieve grid timeseries data as well, and decrease the latency from 118 milliseconds to 89 milliseconds. When it comes to scalar and vector timeseries data insertion, latency was increased a bit. However, we can notice that, the retrieval of scalar and vector timeseries latency improved from 23 milliseconds to 7 milliseconds. Specially, the latency for query location timeseries metadata was improved from 3 milliseconds to 2 milliseconds. It was constant with 3 milliseconds in previous load testings. Other than inserting scalar and vector data, other test cases standard deviation was improved, and we can conclude that the overall system performance is enhanced when auto-scaling is enabled.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1.0\textwidth]{results/obs/all_auto/obs_all_auto_15m_res_latencies_against_hits.png}
    \caption{Latency against server hits while load testing with 15-minute of data with enabled auto-scaling.}
    \label{fi:test_obs_all_auto_15m_latency}
\end{figure}
\cref{fi:test_obs_all_auto_15m_latency} graph provides an overview of the variation of latency over the elapsed time of the test plan against the number of server hits per second for 15-minute data while auto-scaling enabled for \acrshort{k8s}. According to the graph, the \acrshort{wdias} was able to keep the latency constant all over the elapsed time.
When compared to \cref{fi:test_obs_all_15m_latency} without auto-scaling, we can see lesser latency spikes throughout the test period.

@@

\cref{fi:test_obs_all_auto_15m_throughtput} shows the total server's transaction throughput against the number of active threads. When compared to \cref{fi:test_obs_all_15m_throughtput} without auto-scaling, the estimated throughput with a higher number of active threads becomes stable, according to the graph. Thus, we can conclude that enabling auto-scaling also improves the throughput by supporting a higher number of active threads. We can see fluctuation when increase the number of active threads due to lack of sample latency with higher number of active threads during the peak of load testing. Further, we can see estimated throughput for insert and retrieve grid data also increased by a small factor, and it more smooth than 15-minute data load testing without auto-scaling. During the next paragraphs, we will discuss the resource usage while running the test plan while enabling the auto-scaling.

### 2021-01-01 summary/sec_1-conclusions.tex
After Dr. Dilum reviewed the Viva thesis

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. One of attractive feature of microservice architecture is independent nature of microservices enables to design a highly scalable modular system which can use to handle large volumes of data using a large resource pool. Also, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice exposed endpoints to the users which are only focus on supporting a specific operation or functionality which follows the concept of smart endpoints dumb pipes in \cref{subse:dumb_pipes}. For importing different format data into the system, we added microservice for each data format that known as import microservices. Then, these import microservices store the data via an appropriate database adapter microservice after converting to compatible data format. For handling multiple data formats efficiently, we introduced a database structure in WDIAS. Then, users can fetch data in the required format via using export microservices. Further, we enabled integrating extensional microservices which provides the data preprocessing capabilities, and it allow users to integrate new features as new extension microservices. We used geo-index to support geo-based search queries and metadata search queries. Also, the system provides asynchronous request handling based on the request size with maintaining status per request.

@@

We evaluated the performance using a cloud-based setup on the \acrfull{eks}.
Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate. Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, the \acrshort{wdias} was able to provide the same throughput while keeping the latency constant. Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Thus, we can conclude that the system is scalable. With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations. The results of \acrshort{wdias} shows that the system can run on a cluster from few CPU node to nodes with a few hundred CPUs.

>>>>

First, the architecture of \acrshort{wdias} starts with \acrshort{soa} using an \acrfull{esb} and then moved to actor model-based architecture. After comparing the disadvantages of using such architectures with the system requirements, we came up with modern microservice architecture. One of attractive feature of microservice architecture is independent nature of microservices enables to design a highly scalable modular system which can use to handle large volumes of data using a large resource pool. Also, we used many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities. \acrshort{wdias} implemented the microservice architecture on top of the \acrshort{k8s}, which is a container orchestration platform. We mapped each microservice of \acrshort{wdias} to a pod in the \acrshort{k8s} cluster. Also, each microservice exposed endpoints to the users which are only focus on supporting a specific operation or functionality which follows the concept of smart endpoints dumb pipes. For importing different format data into the system, we added microservice for each data format that known as import microservices. Then, these import microservices store the data via an appropriate database adapter microservice after converting to compatible data format. For handling multiple data formats efficiently, we introduced a database structure in WDIAS. Then, users can fetch data in the required format via using export microservices. Further, we enabled integrating extensional microservices which provides the data preprocessing capabilities, and it allow users to integrate new features as new extension microservices. We used geo-index to support geo-based search queries and metadata search queries. Also, the system provides asynchronous request handling based on the request size with maintaining status per request.

Compared to other existing weather data integration and assimilation systems, WDIAS has the advantage of taking full advantage of cloud computing technologies to implement a highly scalable and available system at low-cost. Because it uses containerized applications to implement the microservices, it allows independent service deployments. Each microservice can scale independently without affecting other microservices. Further, each microservice could use a suitable technology stack for the task. \acrshort{fews}, \acrshort{madis}, and \acrshort{msm} have platform dependencies, and some of the deployments are performed by copy-pasting source codes. The \acrshort{fews} and \acrshort{msm} provide a centralized data storage mechanism that  can become a bottleneck while processing a large volume of data in critical situations. \acrshort{madis} and \acrshort{dias} also support data storage arrays to store data. WDIAS and \acrshort{lead} can support a pool of resources based on the requirement.
Like other systems, WDIAS provides data preprocessing capabilities, and users can integrate new data preprocessing capabilities by implementing them as independent containerized microservice applications. Even though \acrshort{fews}, \acrshort{lead}, and \acrshort{msm} provide workflow engine support and model execution support, these can be achieved using an external workflow management system by fulfilling the data requirements via WDIAS. Further, WDIAS is an extendable open framework such that similar capabilities can be integrated as a new extension module system. Compared to other existing systems, the \acrshort{lead} is more scalable and is implemented using \acrshort{soa} architecture. However, with the help of modern container orchestration frameworks, such as Kubernetes and cloud computing technologies, those can provide high scalability and high availability as inherent capabilities. Those are mature enough to provide fault-tolerance automatically \cite{Scolati2019ADevices}. Implementing the deployment units as containerized applications based on the modern architecture patterns allows WDIAS to implement a highly scalable and high available system without heavy effort on those features.  A comparison  between WDIAS and other systems are presented in Table \ref{fi:architecture_comparison}.

@@

We evaluated the performance using a cloud-based setup on the \acrfull{eks}.
Based on the performance analysis, we were able to perform 300 \acrshort{rps}, and the system handled the workload successfully with minimizing the error rate. Also, while we increased the request size from 24 to 96 data points per scalar and vector timeseries, and the number of ASCII Grid files from 24 to 96, \acrshort{wdias} was able to provide the same throughput while keeping the latency constant. Likewise, the system was able to provide an increase in the throughput by keeping the latency constant while increasing the workload. Thus, we can conclude that the system is scalable. With \acrshort{k8s} auto-scaling enabled, the \acrshort{k8s} elastically adjust the number of pods according to the workload with provided auto-scaling configurations. The results of \acrshort{wdias} shows that the system can run on a cluster from few CPU node to nodes with a few hundred CPUs.
